title

### 2016-05-13 paper.tex
paper: notes
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

\begin{figure}[h]
  \centering
    \includegraphics[width=0.45\textwidth]{experiments/objclass-dev/output.png}
    \caption{
[\href{https://github.com/noahdesu/zlog-popper/tree/master/experiments/objclass-dev/visualize.ipynb}{source}]
Growth of officially supported, custom object interfaces in RADOS over 6
years. A \emph{method} is a specific object interface and a \emph{class} is a
logical grouping of methods.
}
\end{figure}

@@

>>>>

Cloud providers are increasingly reliant upon application-specific extensions
to distributed storage system such as Ceph as is shown in
Figure~\ref{fig:objclass-dev} by a marked increase in Ceph extensions used in
production.

The construction of extensions is not limited to core developers; the
development community has been receptive to contributions with the recent
inclusion by CERN developers of an extension for performing limited numeric
operations on object data~\cite{cls_numops}.

This trend is not limited to Ceph. AWS Lambda, Redis Lua, Redis Modules,
KV-Drives, and Rhea, are all recent examples of storage systems embracing the
power of including application-specific semantics. While Ceph has not yet
reached the point of directly exposing these features to users, the recent
inclusion of a mechanism for dynamically defining extensions using
Lua~\cite{cls_lua} suggests that aspects of this may soon appear.

If the growth illustrated in Figure~\ref{fig:objclass-dev} continues, the
amount of low-level C++ is likely to grow very larage. Unfortunately, much of
this code is written assuming a performance profile defined by a combination
of the hardware and software versions available at the time of development. As
Ceph development continues at a fast pace, the cost of adapting to changing
assumptions regarding performance will become significant.

% footnote: we could probably look through the cls_* changelog and find
% examples of changes based on changes to semantics.

% Virtualization. Operating systems and containers are similar. AUFS, dockerfile

In order to avoid this we need declarative magic hats.

\section{Recurring Problem}

Describe CORFU briefly, and then show the physical design challenge. The
performance decision changes depending on the mix of hardware and software
versions and configurations.

@@

\begin{figure}[ht]
  \centering
    \includegraphics[width=0.45\textwidth]{experiments/objclass-dev/output.png}
    \caption{
[\href{https://github.com/noahdesu/zlog-popper/tree/master/experiments/objclass-dev/visualize.ipynb}{source}]
Growth of officially supported, custom object interfaces in RADOS over 6
years. A \emph{method} is a specific object interface and a \emph{class} is a
logical grouping of methods.
}
\label{fig:objclass-dev}
\end{figure}
